Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-10 tex/VHzQ.tex
VHzQ.tex update

The VH$z$Q with the bluest colour in (W1 - W2) is 
DELS J1048-0109 with (W1-W2) = 0.154 
(see Figure~\ref{fig:DELS_J1048).

>>>>

\begin{figure}
    \centering
    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
    {../color_color/W1W2_plots/W1W2W3_hexplots_20190610v2.png} 
  \vspace{-14pt}
    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
      (grey colour-scale). }
    \label{fig:W1W2W3}
\end{figure}

\subsection{MIR Colours}

%% 
%%    (W1 - W2)    vs.  (W2 - W3) 
%% Call W1 ~ 3-4um annd W2   4-5um and   W3 10-16um
Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs. (W2-W3) colour – colour
space diagram showing the WISE colours for the 283 VH$z$Q that have
reported w3mpro values (blue to red coloured points).  400,000 quasars
at redshift $z\lesssim3.0$ from the DR14Q are also shown (grey
colour-scale). 
W1 samples $\approx$0.6-4$\mu$m for the $z=0-3$ quasars, 
W2 samples $\approx$1.25-5$\mu$m for the $z=0-3$ quasars, 
W3 samples $\approx$2.-16$\mu$m for the $z=0-3$ quasars, 
1

%%
The VH$z$Q with the bluest colour in (W1 - W2) is 
DELS J1048-0109 with (W1-W2) = 0.154 
(see Figure~\ref{fig:DELS_J1048}).
